---
title: "Weight of Fish"
author: "Chris Gonzalez"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(leaps)
require(car)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch

### Best Models
```{r}
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
#library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```

Based on the analysis performed using the leaps code, a graphical representation provided valuable insights leading to the determination that the height and width dimensions constitute the most effective combination within the regression model. This conclusion was derived from visual observations and data interpretation facilitated by the graph generated through the analysis.


### Best Two regressor model

```{r}
best.model <- lm(Weight~Height+Width,data=Perch)
summary(best.model)
```

The optimal approach for determining the weight of a perch fish involves employing the most influential components within the regression model. In this instance, the Perch fish exhibits an adjusted R-squared value of 0.94, achieved through the refinement of the analysis to encompass solely the dimensions of height and width.

## Pike

### Best Models
```{r}
regsubsets.outpike <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
summary.outpike <- summary(regsubsets.outpike)
as.data.frame(summary.outpike$outmat)
#library(car)
subsets(regsubsets.outpike,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

By leveraging the graphical representation of the regression model, the analysis highlights the optimal combination of variables to employ. In this specific scenario, the visual depiction indicates that the most effective model encompasses the variables length 1, length 2, length 3, height, and width of the pike fish. The graph assists in visually identifying these variables as the key factors for accurate predictions and reliable outcomes within the regression analysis.


### Best Two regressor model
```{r}
pikebesttwo <- lm(Weight~Length1+Length3,data=Pike)
summary(pikebesttwo)
```
Through careful analysis of the graph, it has been determined that the best 2 regression model consists of length 1 and length 3 as its two key variables. This conclusion is supported by an impressive adjusted R-squared value of 0.9649, indicating a high level of goodness-of-fit and predictive accuracy. By focusing on these specific variables, the regression model yields substantial explanatory power and enhances the precision of weight estimation for the pike fish.

## Roach

### Best Models
```{r}
regsubsets.outroach <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
summary.out <- summary(regsubsets.outroach)
as.data.frame(summary.out$outmat)
#library(car)
subsets(regsubsets.outroach,statistic="adjr2",legend="topright",main="Adjusted R^2")
```
Based on the analysis conducted using the leaps shortcut code, it has been determined that the most optimal regression model comprises the variables Length 3 and Width. This conclusion is derived from the graphical representation provided by the code, which indicates that these two variables yield the best results in terms of model performance. By focusing on Length 3 and Width as key predictors, the regression model exhibits a higher degree of accuracy and provides valuable insights for estimating the weight of the roach fish.


### Best Two regressor model

```{r}
best.modelroach <- lm(Weight~Length3+Width,data=Roach)
summary(best.modelroach)
```
The analysis supports the notion that the best two-variable regression model coincides with the overall best regression model, both featuring Length 3 and Width as the chosen variables. This alignment is further validated by an adjusted R-squared value of 0.8482, which signifies a strong degree of explanatory power and predictive capability for the model. The utilization of Length 3 and Width as key predictors enhances the accuracy and reliability of weight estimation for the roach fish.



## Final Summary Statements
Based on an extensive analysis utilizing leaps for a graphical representations, it has been determined that selecting the most effective regression model for accurately estimating the weight of the fish necessitates considering the two best variables within the model. These variables consistently exhibit exceptional performance in terms of predictive accuracy, as indicated by their notably high adjusted R-squared values. Their inclusion within the regression model significantly enhances its explanatory power, resulting in reliable outcomes for fish weight predictions. For the Perch fish, the two optimal variables were identified as height and width. Similarly, for the Pike fish, the best variables were found to be length 1 and length 3. Lastly, for the Roach fish, the most influential variables were determined to be length 3 and width.




